Evolution of ORM Systems: Formal Foundations

### 2013-02-02 doc/description.tex
primary key has a sequence

\paragraph{Mapping of Classes} The class is mapped into a table with  automatically created primary key. The primary key is always created with name Id and of the $\mathbb{N^{*}}$ type. The properties and associations has to be mapped separately.
\begin{align*}
&	\mathbf{\rho_{c}} : Class*  \rightarrow Table* \\
&	\rho_{c}(c) = %\begin{cases}
		%\inference{c = \varnothing}{\varnothing}\\\\
		%\inference{|c| > 1}{\rho_c(head(c)) \cup \rho_c(tail(c))} \\ \\
		\inference{|c| = 1}{table(name(c), primaryKey("Id"), \varnothing, \varnothing)} % \end{cases} 
\\ 	
& c \in Class*
\end{align*}

@@

There can occur name collision during mapping in case there are more classes with property representing collection. To avoid that the mapping changes the name of the table representing a collection.
\begin{align*}
&	\mathbf{\rho_p} : Property* \rightarrow Column* \\ \\
&	\rho_{sp}(p) = \begin{cases}
		%\inference{p = \varnothing}{\varnothing}\\
		%\inference{|p| > 1}{\rho_{sp}(head(p)) \cup \rho_{sp}(tail(p))}\\\\
 		\inference{|p| = 1 \wedge cardinality(p) = 1 \wedge !\;mandatory(p)
 			\\ \wedge \exists t = table(name(owningClass(p)), d) 
		 }{\begin{gathered}
	  		col(name(p), \rho_t(type(p)), \varnothing )
		\end{gathered}} \\ \\
  		\inference{|p| = 1 \wedge cardinality(p) = 1 \wedge mandatory(p)
			 \\ \wedge \exists t = table(name(owningClass(p)), d)
			\\ \wedge ! instanciated(owningClass(p))
		}{\begin{gathered}
 	 		col(name(p), \rho_t(type(p)), NOTNULL ) \\ 
		\end{gathered}}
	\end{cases}\\
&	p \in Property
\end{align*}
\begin{align*}
&	\mathbf{\rho_p} : Property* \rightarrow Table* \\ \\
&	\rho_{cp}(p) = \\
& \;\;\;\;\;\; =\begin{cases}
		%\inference{p = \varnothing}{\varnothing}\\
		%\inference{|p| > 1}{\rho_{cp}(head(p)) \cup \rho_{cp}(tail(p))}\\\\
     	\inference{|p| = 1 \wedge cardinality(p) > 1 \wedge !\;mandatory(p) \\ 
     		\wedge 	\exists t = table(name(owningClass(p)), d)
     		}{\begin{gathered}
     			tab(name(p), primaryKey("Id"), \\ col("value", \rho_t(type(p)), \varnothing), \\ fk(name(p), 			name(owningClass(p)), NOTNULL) \\
    	\end{gathered}}\\ \\
     	\inference{|p| = 1 \wedge  cardinality(p) > 1 \wedge mandatory(p) \\ 
     		\wedge \exists t = table(name(owningClass(p)), d) 
     		}{\begin{gathered}  
     			tab(name(p), primaryKey("Id"), \\ 
     			col("value", \rho_t(type(p)), NOTNULL), \\ 			fk(name(p), name(owningClass(p)), NOTNULL)
    	 \end{gathered}}
 	\end{cases}\\
& 	p \in Property
\end{align*}

\paragraph{Mapping of Associations} An association is mapped into database as a foreign key in table representing associated class or as a table in case the association cardinality is one to many or many to many. Thus there are two mapping cases as for properties and the same solution is used to avoid name collisions.
\begin{align*}
&	\mathbf{\rho_a} : Association* \rightarrow ForeignKey* \\
&	\rho_a(a) = \begin{cases}
		%\inference{a = \varnothing}{\varnothing}\\
		%\inference{|a| > 1}{\rho_{a}(head(a)) \cup \rho_{a}(tail(a))}\\\\
		\inference{|a| = 1 \wedge  startCardinality(a) = 0 \\ \wedge \exists t \in table(name(owningClass(p)), d) \\ \wedge \exists u : u = table(reference(a)), d)
		}{
			fk(name(a), name(t),  \varnothing) 
	 	}
  \\ \\
 	 \inference{|a| = 1 \wedge  startCardinality(a) = 1 \\ \wedge \exists t = tab(name(owningClass(p)), d) \\ \wedge \exists u \in tables(d) : name(u = reference(a)
 	 }{ 
		fk(name(a), name(t),  NOTNULL)
	}	 \end{cases}
\\
&	 a \in Association
\end{align*}
\begin{align*} 
&	\mathbf{\rho_a} : Association* \rightarrow Table* \\
&	\rho_a(a) =
% 	  \begin{cases}
 		%\inference{a = \varnothing}{\varnothing}\\
		%\inference{|a| > 1}{\rho_{a}(head(a)) \cup \rho_{a}(tail(a))}\\\\
		\inference{|a| = 1 \wedge   startCardinality > 1 \\ \wedge \exists t \in tables(d) : name(owningClass(p)) = name(t) \\ \wedge \exists e \in tables(d) : name(reference(a)) = name(e)
  		}{\begin{gathered}  
		 table(name(a), pk("Id"), \varnothing, \\ fk(name(owningClass(a)), \\ name(owningClass(a)), NOTNULL) \\ fk(reference(a), reference(a), NOTNULL)) 
  		\end{gathered}}  
 	%\end{cases}
\\
&	 a \in Association
\end{align*}

@@

\newpage
Initial state of the software:
\medskip
\hline
\begin{align*}
&	S = sw(a, db(t,r))
\end{align*}
\begin{align*}
a &= app(cl(Person, (pr(surname, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalParty, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing))
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id"), col(surname, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalParty, pk("Id"),  col(businessName, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing)) 
\end{align*}
\begin{align*}
r &= row("person", ["Id", 1], ["surname", "Griffin"], \\
& ["street", "S. Mary Evenue 22"], ["city", "NY"], ["zip", 10001]), \\
& row("person", ["Id", 2], ["surname", "Doe"], \\
& ["street", "Olive ave. 2225"], ["city", "LA"], ["zip", 90003]), \\
& row("LegalParty", ["Id", 10], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("LegalParty", ["Id", 20], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003]))
\end{align*}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{align*}
S_1 &= state(S) \oplus \mathbf{addClass}(cl("Address\_tmp1", \varnothing, \varnothing)) \\
& \oplus MoveProperty("Person", "Address\_tmp1", "street", "city", "zip", \\
& \;\;\;\;\;\; \;\;\;\;\;\;    \{(x,x) | x \in instances("Person", database(S))\}) \\
& \;\;\;\;\;\; \oplus AddAssociation("Person", \\ 
& \;\;\;\;\;\;\;\;\;\;\;\; assoc("address", "Address\_tmp1", 1, 1),\\ 
& \;\;\;\;\;\;\;\;\;\;\;\; \{(x,y)| x \in instances("Person", database(S)), \\
& \;\;\;\;\;\; \;\;\;\;\;\; y \in instances("Address\_tmp1", database(S)) : \\ 
& \;\;\;\;\;\;\;\;\;\;\;\; pkVal(x) = pkVal(y) \})
\end{align*}
\hline
\begin{align*}
a' &= app(cl(Person, (pr(surname, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalParty, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)),\\
& \mathbf{cl("Address\_tmp1", \varnothing, \varnothing)}
 )
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id"), col(surname, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalParty, pk("Id"),  col(businessName, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& \mathbf{tab("Address\_tmp1", pk("Id"), \varnothing, \varnothing)}) 
\end{align*}
%\begin{align*}
%r &= row("person", ["Id", 1], ["surname", "Griffin"], \\
%& ["street", "S. Mary Evenue 22"], ["city", "NY"], ["zip", 10001]), \\
%& row("person", ["Id", 2], ["surname", "Doe"], \\
%& ["street", "Olive ave. 2225"], ["city", "LA"], ["zip", 90003]), \\
%& row("LegalParty", ["Id", 10], \\
%& ["businessName", "Tools and Machines ltd."], \\
%& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
%& row("LegalParty", ["Id", 20], ["businessName", "Doe"], \\
%& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003]))
%\end{align*}

@@

\hline
\begin{align*}
a' &=app(cl(Person, (pr(surname, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalParty, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl("Address\_tmp1", \mathbf{pr(street, APPSTRING, \varnothing)} , \varnothing)
& )
\end{align*}
\begin{align*}
t &=db(tab(Person, pk("Id"), col(surname, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalParty, pk("Id"),  col(businessName, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab("Address\_tmp1", pk("Id"), \mathbf{col(street, APPSTRING, \varnothing, \varnothing)},\\
& \varnothing)) 
\end{align*}
%\begin{align*}
%r &=\{ row("person", ["Id", 1], ["surname", "Griffin"], \\
%& ["street", "S. Mary Evenue 22"], ["city", "NY"], ["zip", 10001]), \\
%& row("person", ["Id", 2], ["surname", "Doe"], \\
%& ["street", "Olive ave. 2225"], ["city", "LA"], ["zip", 90003]), \\
%& row("LegalParty", ["Id", 10], ["businessName", "Tools and Machines ltd."], \\
%& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
%& row("LegalParty", ["Id", 20], ["businessName", "Doe"], \\
%& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003])\\
%& row("address\_tmp1", ["Id", 1], ["street", "S. Mary Evenue 22"]) \\
%& row("address\_tmp1", ["Id", 1], ["street", "Olive ave. 2225"] )\\
%\}
%\end{align*}

@@

%t &=db(tab(Person, pk("Id"), col(surname, APPSTRING, \varnothing, \varnothing), \\

@@

%& tab(LegalParty, pk("Id"),  col(businessName, APPSTRING, \varnothing, \varnothing), \\

@@

%& tab("Address\_tmp1", pk("Id"), col(street, APPSTRING, \varnothing, \varnothing),\\

@@

%t &=db(tab(Person, pk("Id"), col(surname, DBSTRING, \varnothing, \varnothing), \\

@@

%& tab(LegalParty, pk("Id"),  col(businessName, DBSTRING, \varnothing, \varnothing), \\

@@

%& tab("Address\_tmp1", pk("Id"), col(street, DBSTRING, \varnothing, \varnothing),\\

@@

t &=db(tab(Person, pk("Id"), col(surname, DBSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalParty, pk("Id"),  col(businessName, DBSTRING, \varnothing, \varnothing), \\

@@

& \mathbf{tab("Address\_tmp1", pk("Id"), col(street, DBSTRING, \varnothing, \varnothing),}\\

@@

\hline
\begin{align*}
a' &= app(cl(Person, (pr(surname, APPSTRING, \varnothing)), \\ 
& \mathbf{assoc("address", "Address\_tmp1", 1, 1)}), \\ 
& cl(LegalParty, pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing), pr(zip, APPSTRING, \varnothing)), \\
& cl("Address\_tmp1", pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing), pr(zip, APPSTRING, \varnothing), \varnothing)
& )
\end{align*}
\begin{align*}
t' &=db(tab(Person, pk("Id"), col(surname, DBSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalParty, pk("Id"),  col(businessName, DBSTRING, \varnothing, \varnothing), \\
& col(street, DBSTRING, \varnothing, \varnothing), col(city, DBSTRING, \varnothing, \varnothing) \\
& col(zip, DBSTRING, \varnothing, \varnothing), \varnothing), \\
& tab("Address\_tmp1", pk("Id"), col(street, DBSTRING, \varnothing, \varnothing),\\
& col(city, DBSTRING, \varnothing, \varnothing), col(zip, DBSTRING, \varnothing, \varnothing) \\
& \mathbf{fk("person\_address", "Person", \varnothing)})\\
) 
\end{align*}
\begin{align*}
r &=\{ row("person", ["Id", 1], ["surname", "Griffin"]), \\
& row("person", ["Id", 2], ["surname", "Doe"]), \\
& row("LegalParty", ["Id", 10], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("LegalParty", ["Id", 20], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003])\\
& row("address\_tmp1", ["Id", 1], ["street", "S. Mary Evenue 22"], \\
& ["city", "NY"], ["zip", 10001], \mathbf{["person\_address", 1]}) \\
& row("address\_tmp1", ["Id", 2], ["street", "Olive ave. 2225"], \\
& ["city", "LA"], ["zip", 90003], \mathbf{["person\_address", 2]}) )\\
\}
\end{align*}

>>>>

\paragraph{Mapping of Classes} The class is mapped into a table with  automatically created primary key. The primary key is always created with name Id and of the $\mathbb{N^{*}}$ type. The properties and associations has to be mapped separately.
\begin{align*}
&	\mathbf{\rho_{c}} : Class*  \rightarrow Table* \\
&	\rho_{c}(c) = %\begin{cases}
		%\inference{c = \varnothing}{\varnothing}\\\\
		%\inference{|c| > 1}{\rho_c(head(c)) \cup \rho_c(tail(c))} \\ \\
		\inference{|c| = 1}{table(name(c), primaryKey("Id", s_1), \varnothing, \varnothing)} % \end{cases} 
\\ 	
& c \in Class*
\end{align*}

@@

There can occur name collision during mapping in case there are more classes with property representing collection. To avoid that the mapping changes the name of the table representing a collection.
\begin{align*}
&	\mathbf{\rho_p} : Property* \rightarrow Column* \\ \\
&	\rho_{sp}(p) = \begin{cases}
		%\inference{p = \varnothing}{\varnothing}\\
		%\inference{|p| > 1}{\rho_{sp}(head(p)) \cup \rho_{sp}(tail(p))}\\\\
 		\inference{|p| = 1 \wedge cardinality(p) = 1 \wedge !\;mandatory(p)
 			\\ \wedge \exists t = table(name(owningClass(p)), d) 
		 }{\begin{gathered}
	  		col(name(p), \rho_t(type(p)), \varnothing )
		\end{gathered}} \\ \\
  		\inference{|p| = 1 \wedge cardinality(p) = 1 \wedge mandatory(p)
			 \\ \wedge \exists t = table(name(owningClass(p)), d)
			\\ \wedge ! instanciated(owningClass(p))
		}{\begin{gathered}
 	 		col(name(p), \rho_t(type(p)), NOTNULL ) \\ 
		\end{gathered}}
	\end{cases}\\
&	p \in Property
\end{align*}
\begin{align*}
&	\mathbf{\rho_p} : Property* \rightarrow Table* \\ \\
&	\rho_{cp}(p) = \\
& \;\;\;\;\;\; =\begin{cases}
		%\inference{p = \varnothing}{\varnothing}\\
		%\inference{|p| > 1}{\rho_{cp}(head(p)) \cup \rho_{cp}(tail(p))}\\\\
     	\inference{|p| = 1 \wedge cardinality(p) > 1 \wedge !\;mandatory(p) \\ 
     		\wedge 	\exists t = table(name(owningClass(p)), d)
     		}{\begin{gathered}
     			tab(name(p), primaryKey("Id", s_1), \\ col("value", \rho_t(type(p)), \varnothing), \\ fk(name(p), 			name(owningClass(p)), NOTNULL) \\
    	\end{gathered}}\\ \\
     	\inference{|p| = 1 \wedge  cardinality(p) > 1 \wedge mandatory(p) \\ 
     		\wedge \exists t = table(name(owningClass(p)), d) 
     		}{\begin{gathered}  
     			tab(name(p), primaryKey("Id", s_1), \\ 
     			col("value", \rho_t(type(p)), NOTNULL), \\ 			fk(name(p), name(owningClass(p)), NOTNULL)
    	 \end{gathered}}
 	\end{cases}\\
& 	p \in Property
\end{align*}

\paragraph{Mapping of Associations} An association is mapped into database as a foreign key in table representing associated class or as a table in case the association cardinality is one to many or many to many. Thus there are two mapping cases as for properties and the same solution is used to avoid name collisions.
\begin{align*}
&	\mathbf{\rho_a} : Association* \rightarrow ForeignKey* \\
&	\rho_a(a) = \begin{cases}
		%\inference{a = \varnothing}{\varnothing}\\
		%\inference{|a| > 1}{\rho_{a}(head(a)) \cup \rho_{a}(tail(a))}\\\\
		\inference{|a| = 1 \wedge  startCardinality(a) = 0 \\ \wedge \exists t \in table(name(owningClass(p)), d) \\ \wedge \exists u : u = table(reference(a)), d)
		}{
			fk(name(a), name(t),  \varnothing) 
	 	}
  \\ \\
 	 \inference{|a| = 1 \wedge  startCardinality(a) = 1 \\ \wedge \exists t = tab(name(owningClass(p)), d) \\ \wedge \exists u \in tables(d) : name(u = reference(a)
 	 }{ 
		fk(name(a), name(t),  NOTNULL)
	}	 \end{cases}
\\
&	 a \in Association
\end{align*}
\begin{align*} 
&	\mathbf{\rho_a} : Association* \rightarrow Table* \\
&	\rho_a(a) =
% 	  \begin{cases}
 		%\inference{a = \varnothing}{\varnothing}\\
		%\inference{|a| > 1}{\rho_{a}(head(a)) \cup \rho_{a}(tail(a))}\\\\
		\inference{|a| = 1 \wedge   startCardinality > 1 \\ \wedge \exists t \in tables(d) : name(owningClass(p)) = name(t) \\ \wedge \exists e \in tables(d) : name(reference(a)) = name(e)
  		}{\begin{gathered}  
		 table(name(a), pk("Id", s_1), \varnothing, \\ fk(name(owningClass(a)), \\ name(owningClass(a)), NOTNULL) \\ fk(reference(a), reference(a), NOTNULL)) 
  		\end{gathered}}  
 	%\end{cases}
\\
&	 a \in Association
\end{align*}

@@

\newpage
Initial state of the software:
\medskip
\hline
\begin{align*}
&	S = sw(a, db(t,r))
\end{align*}
\begin{align*}
a &= app(cl(Person, (pr(surname, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalParty, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing))
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id", s_1), col(surname, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalParty, pk("Id", s_1),  col(businessName, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing)) 
\end{align*}
\begin{align*}
r &= row("person", ["Id", 1], ["surname", "Griffin"], \\
& ["street", "S. Mary Evenue 22"], ["city", "NY"], ["zip", 10001]), \\
& row("person", ["Id", 2], ["surname", "Doe"], \\
& ["street", "Olive ave. 2225"], ["city", "LA"], ["zip", 90003]), \\
& row("LegalParty", ["Id", 10], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("LegalParty", ["Id", 20], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003]))
\end{align*}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{align*}
S_1 &= state(S) \oplus \mathbf{addClass}(cl("Address\_tmp1", \varnothing, \varnothing)) \\
& \oplus MoveProperty("Person", "Address\_tmp1", "street", "city", "zip", \\
& \;\;\;\;\;\; \;\;\;\;\;\;    \{(x,x) | x \in instances("Person", database(S))\}) \\
& \;\;\;\;\;\; \oplus AddAssociation("Person", \\ 
& \;\;\;\;\;\;\;\;\;\;\;\; assoc("address", "Address\_tmp1", 1, 1),\\ 
& \;\;\;\;\;\;\;\;\;\;\;\; \{(x,y)| x \in instances("Person", database(S)), \\
& \;\;\;\;\;\; \;\;\;\;\;\; y \in instances("Address\_tmp1", database(S)) : \\ 
& \;\;\;\;\;\;\;\;\;\;\;\; pkVal(x) = pkVal(y) \})
\end{align*}
\hline
\begin{align*}
a' &= app(cl(Person, (pr(surname, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalParty, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)),\\
& \mathbf{cl("Address\_tmp1", \varnothing, \varnothing)}
 )
\end{align*}
\begin{align*}
t &= db(tab(Person, pk("Id", s_1), col(surname, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalParty, pk("Id", s_1),  col(businessName, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& \mathbf{tab("Address\_tmp1", pk("Id", s_1), \varnothing, \varnothing)}) 
\end{align*}
%\begin{align*}
%r &= row("person", ["Id", 1], ["surname", "Griffin"], \\
%& ["street", "S. Mary Evenue 22"], ["city", "NY"], ["zip", 10001]), \\
%& row("person", ["Id", 2], ["surname", "Doe"], \\
%& ["street", "Olive ave. 2225"], ["city", "LA"], ["zip", 90003]), \\
%& row("LegalParty", ["Id", 10], \\
%& ["businessName", "Tools and Machines ltd."], \\
%& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
%& row("LegalParty", ["Id", 20], ["businessName", "Doe"], \\
%& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003]))
%\end{align*}

@@

\hline
\begin{align*}
a' &=app(cl(Person, (pr(surname, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl(LegalParty, (pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing)), pr(zip, APPSTRING, \varnothing)), \\
& cl("Address\_tmp1", \mathbf{pr(street, APPSTRING, \varnothing)} , \varnothing)
& )
\end{align*}
\begin{align*}
t &=db(tab(Person, pk("Id", s_1), col(surname, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalParty, pk("Id", s_1),  col(businessName, APPSTRING, \varnothing, \varnothing), \\
& col(street, APPSTRING, \varnothing, \varnothing), col(city, APPSTRING, \varnothing, \varnothing) \\
& col(zip, APPSTRING, \varnothing, \varnothing), \varnothing), \\
& tab("Address\_tmp1", pk("Id", s_1), \mathbf{col(street, APPSTRING, \varnothing, \varnothing)},\\
& \varnothing)) 
\end{align*}
%\begin{align*}
%r &=\{ row("person", ["Id", 1], ["surname", "Griffin"], \\
%& ["street", "S. Mary Evenue 22"], ["city", "NY"], ["zip", 10001]), \\
%& row("person", ["Id", 2], ["surname", "Doe"], \\
%& ["street", "Olive ave. 2225"], ["city", "LA"], ["zip", 90003]), \\
%& row("LegalParty", ["Id", 10], ["businessName", "Tools and Machines ltd."], \\
%& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
%& row("LegalParty", ["Id", 20], ["businessName", "Doe"], \\
%& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003])\\
%& row("address\_tmp1", ["Id", 1], ["street", "S. Mary Evenue 22"]) \\
%& row("address\_tmp1", ["Id", 1], ["street", "Olive ave. 2225"] )\\
%\}
%\end{align*}

@@

%t &=db(tab(Person, pk("Id", s_1), col(surname, APPSTRING, \varnothing, \varnothing), \\

@@

%& tab(LegalParty, pk("Id", s_1),  col(businessName, APPSTRING, \varnothing, \varnothing), \\

@@

%& tab("Address\_tmp1", pk("Id", s_1), col(street, APPSTRING, \varnothing, \varnothing),\\

@@

%t &=db(tab(Person, pk("Id", s_1), col(surname, DBSTRING, \varnothing, \varnothing), \\

@@

%& tab(LegalParty, pk("Id", s_1),  col(businessName, DBSTRING, \varnothing, \varnothing), \\

@@

%& tab("Address\_tmp1", pk("Id", s_1), col(street, DBSTRING, \varnothing, \varnothing),\\

@@

t &=db(tab(Person, pk("Id", s_1), col(surname, DBSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalParty, pk("Id", s_1),  col(businessName, DBSTRING, \varnothing, \varnothing), \\

@@

& \mathbf{tab("Address\_tmp1", pk("Id", s_1), col(street, DBSTRING, \varnothing, \varnothing),}\\

@@

\hline
\begin{align*}
a' &= app(cl(Person, (pr(surname, APPSTRING, \varnothing)), \\ 
& \mathbf{assoc("address", "Address\_tmp1", 1, 1)}), \\ 
& cl(LegalParty, pr(businessName, APPSTRING, \varnothing), \\
& pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing), pr(zip, APPSTRING, \varnothing)), \\
& cl("Address\_tmp1", pr(street, APPSTRING, \varnothing), \\
& pr(city, APPSTRING, \varnothing), pr(zip, APPSTRING, \varnothing), \varnothing)
& )
\end{align*}
\begin{align*}
t' &=db(tab(Person, pk("Id", s_1), col(surname, DBSTRING, \varnothing, \varnothing), \varnothing), \\
& tab(LegalParty, pk("Id", s_1),  col(businessName, DBSTRING, \varnothing, \varnothing), \\
& col(street, DBSTRING, \varnothing, \varnothing), col(city, DBSTRING, \varnothing, \varnothing) \\
& col(zip, DBSTRING, \varnothing, \varnothing), \varnothing), \\
& tab("Address\_tmp1", pk("Id", s_1), col(street, DBSTRING, \varnothing, \varnothing),\\
& col(city, DBSTRING, \varnothing, \varnothing), col(zip, DBSTRING, \varnothing, \varnothing) \\
& \mathbf{fk("person\_address", "Person", \varnothing)})\\
) 
\end{align*}
\begin{align*}
r &=\{ row("person", ["Id", 1], ["surname", "Griffin"]), \\
& row("person", ["Id", 2], ["surname", "Doe"]), \\
& row("LegalParty", ["Id", 10], ["businessName", "Tools and Machines ltd."], \\
& ["street", "Hill stret 22"], ["city", "NY"], ["zip", 10001]), \\
& row("LegalParty", ["Id", 20], ["businessName", "Doe"], \\
& ["street", "Pine ave. 2225"], ["city", "LA"], ["zip", 90003])\\
& row("address\_tmp1", ["Id", 1], ["street", "S. Mary Evenue 22"], \\
& ["city", "NY"], ["zip", 10001], \mathbf{["person\_address", 1]}) \\
& row("address\_tmp1", ["Id", 2], ["street", "Olive ave. 2225"], \\
& ["city", "LA"], ["zip", 90003], \mathbf{["person\_address", 2]}) )\\
\}
\end{align*}
